---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: "Helvetica Neue", Arial, sans-serif;
  background-color: #f5f7fa;
  color: #333333;
  line-height: 1.6;
}

h1, h2, h3 {
  color: #2c3e50;
  font-weight: bold;
}

h1 {
  text-align: center;
  border-bottom: 3px solid #3498db;
  padding-bottom: 10px;
}

pre, code {
  background-color: #1e1e1e;
  color: #00ffcc;
  border-radius: 8px;
  padding: 10px;
}
}
```

## Handrail holding data

My data is to explore the pattern of whether people hold the handrail when they use stairs.

I collected the group size data: this is to see when people walk on stairs in groups, whether there's any pattern on handrail holding.

There's also data on whether people's hands are empty and how that affects the handrail holding.

```{r}
library(tidyverse)
file_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vR1BavVbYWBXSALcglqptWMrTA0jPJ2qFF7NtlZIFLnr1lnSkUlG9vgLfTCyxmrmbvnifWx6kH_WpbW/pub?gid=793996782&single=true&output=csv"
logged_data <- read.csv(file_url)

```

```{r}
# rename the attributes
latest_data <- logged_data %>%
  rename(
    hold_rail = 2,
    hand_empty = 3,
    group_size = 4
  )

```

```{r}
# some interesting key numbers
no_of_records <- 
  length(latest_data$hold_rail)
max_group_size <- 
  max(latest_data$group_size)
min_group_size <- 
  min(latest_data$group_size)

yes_count <- sum(latest_data$hold_rail == "Yes", na.rm = TRUE)
no_count  <- sum(latest_data$hold_rail == "No", na.rm = TRUE)

```

```{r}
# two charts: 
# 1st one is to see how the group size affect the rail holding decision
latest_data %>%
  ggplot(aes(fill = hold_rail, x = group_size)) +
  geom_bar() +
  theme_minimal() +
  labs(title = "Do they hold the handrail more as group size increases?", subtitle = "STATS 220, 2026",
       x = "group size", 
       fill = "did they hold the rail") +
  theme(legend.position = "bottom", legend.direction = "vertical") 

# 2nd one is to see when people hold the rail or not, if their hands are empty
# Interesting to note when both of their hands are full, they are definitely not holding the hand rail!
latest_data %>%
  ggplot(aes(fill = hand_empty, x = hold_rail)) +
  geom_bar() +
  theme_minimal() +
  labs(title = "Do they hold the handrail when their hands are empty?", subtitle = "STATS 220, 2026",
       x = "did they hold the rail", 
       fill = "are their hands empty") +
  theme(legend.position = "bottom", legend.direction = "vertical") +
  coord_flip()

```

I have collect in total `r no_of_records` responses.

The group size ranges from `r min_group_size` to `r max_group_size`.

In summary, there are `r yes_count` people held the hand rail, while far more people (`r no_count`) didn't.
